Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-27 methods-and-results.Rmd
:construction: sample Ns

rbind(
  missS1,
  missS2,
  missS3
) %>%
  mutate(study = c(1, 2, 3)) %>%
  select(study, everything()) %>%
  kbl(.,
      escape = FALSE,
      booktabs = TRUE,
      align = "c", #c("l", rep("c", ncol(.)-1)),
      col.names = c("Study", rep(c("Full","Reduced","$\\Delta$", "%"), 3)),
      digits=2,
      caption = "Missingness Info by Study") %>%
  add_header_above(c(" " = 1, "Measurements" = 4, "Participants" = 4, "Timepoints" = 4)) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

Something about the migration experience literature should go here as part of the illustration intro ...

\subsection{Data}
We used a data set following migration experiences collected by \citet[][]{Kreienkamp2022b}. The data set consisted of three individual studies that followed migrants who had recently arrived in the Netherlands in their daily interactions with the Dutch majority group. After a general migration-focused pre-questionnaire, participants were invited twice per day to report on their (potential) interactions with majority group members for at least 30 days. The short ESM surveys were sent out at around lunch (12pm) and dinner time (7pm). After the 30 day study period participants filled in a post-questionnaire that mirrored the pre-questionnaire. Participants received either monetary compensation or partial course credits based on the number of surveys they completed. For our empirical example we focused on the variables that were collected during the ESM surveys and were available for all three studies. Full methodological details are available in the article by \citet[][]{Kreienkamp2022b}.

\subsubsection{Sample and time frame (?)}

filter criteria
\citep[proportion of missing data and imputations:][]{Madley-Dowd2019}

>>>>

missS123 <- rbind(
  missS1,
  missS2,
  missS3
) %>%
  mutate(study = c(1, 2, 3)) %>%
  select(study, everything())

missS123 %>%
  kbl(.,
      escape = FALSE,
      booktabs = TRUE,
      align = "c", #c("l", rep("c", ncol(.)-1)),
      col.names = c("Study", rep(c("Full","Reduced","$\\Delta$", "%"), 3)),
      digits=2,
      caption = "Missingness Info by Study") %>%
  add_header_above(c(" " = 1, "Measurements" = 4, "Participants" = 4, "Timepoints" = 4)) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

\subsection{Data}
We used a data set following migration experiences collected by \citet[][]{Kreienkamp2022b}. The data set consists of three studies that followed migrants who had recently arrived in the Netherlands in their daily interactions with the Dutch majority group members. After a general migration-focused pre-questionnaire, participants were invited twice per day to report on their (potential) interactions with majority group members for at least 30 days. The short ESM surveys were sent out at around lunch (12pm) and dinner time (7pm). After the 30 day study period participants filled in a post-questionnaire that mirrored the pre-questionnaire. Participants received either monetary compensation or partial course credits based on the number of surveys they completed. For our empirical example we focus on the variables that were collected during the ESM surveys and were available in all three studies. Full methodological details are available in the empirical article by \citet[][]{Kreienkamp2022b}.

\subsubsection{Sample}
The original studies included `r sum(missS123$pptFull)` participants ($N_{S1}=$`r missS123$pptFull[missS123$study==1]`, $N_{S2}=$`r missS123$pptFull[missS123$study==2]`, $N_{S3}=$`r missS123$pptFull[missS123$study==3]`) with a total `r format(sum(missS123$nFull), big.mark=",")` measurements. The studies differed substantially in the maximum length of participation ($N_{t:S1}=$`r missS123$timeFull[missS123$study==1]`, $N_{t:S2}=$`r missS123$timeFull[missS123$study==2]`, $N_{t:S3}=$`r missS123$timeFull[missS123$study==3]`).

\citep[proportion of missing data and imputations:][]{Madley-Dowd2019}

### 2022-11-27 methods-and-results.tex
:construction: sample Ns

Something about the migration experience literature should go here as
part of the illustration intro \ldots{}

@@

We used a data set following migration experiences collected by
\citet[][]{Kreienkamp2022b}. The data set consisted of three individual
studies that followed migrants who had recently arrived in the
Netherlands in their daily interactions with the Dutch majority group.
After a general migration-focused pre-questionnaire, participants were
invited twice per day to report on their (potential) interactions with
majority group members for at least 30 days. The short ESM surveys were
sent out at around lunch (12pm) and dinner time (7pm). After the 30 day
study period participants filled in a post-questionnaire that mirrored
the pre-questionnaire. Participants received either monetary
compensation or partial course credits based on the number of surveys
they completed. For our empirical example we focused on the variables
that were collected during the ESM surveys and were available for all
three studies. Full methodological details are available in the article
by \citet[][]{Kreienkamp2022b}.

\subsubsection{Sample and time frame (?)}

filter criteria
\citep[proportion of missing data and imputations:][]{Madley-Dowd2019}

>>>>

@@

We used a data set following migration experiences collected by
\citet[][]{Kreienkamp2022b}. The data set consists of three studies that
followed migrants who had recently arrived in the Netherlands in their
daily interactions with the Dutch majority group members. After a
general migration-focused pre-questionnaire, participants were invited
twice per day to report on their (potential) interactions with majority
group members for at least 30 days. The short ESM surveys were sent out
at around lunch (12pm) and dinner time (7pm). After the 30 day study
period participants filled in a post-questionnaire that mirrored the
pre-questionnaire. Participants received either monetary compensation or
partial course credits based on the number of surveys they completed.
For our empirical example we focus on the variables that were collected
during the ESM surveys and were available in all three studies. Full
methodological details are available in the empirical article by
\citet[][]{Kreienkamp2022b}.

\subsubsection{Sample}

The original studies included 207 participants (\$N\_\{S1\}=\$23,
\$N\_\{S2\}=\$113,
\$N\_\{S3\}=\(71) with a total 10,297 measurements. The studies differed substantially in the maximum length of participation (\)N\_\{t:S1\}=\$63,
\$N\_\{t:S2\}=\$69, \$N\_\{t:S3\}=\$155).

\citep[proportion of missing data and imputations:][]{Madley-Dowd2019}
